---
title: "Schrott"
output: github_document
---

## StARS Simulation (Liu et al. 2010)
* **Graph Structure:** The matrix rows/columns are partitioned into J equally-sized disjoint groups.
* **Groups:** Groups are denoted as V_1, V_2, ..., V_J such that their union forms the
set of all indices: V_1 U V_2 U ... U V_J = {1, ..., p}.
* **Pivotal Row:** Each of these groups V_k has an associated "pivotal" row denoted by k.
* **Size of Group:** The size of group V_1 is represented as s.
* **Omega (Precision Matrix) Structure:** For any index i in group V_k, the precision matrix elements Ω_ik and Ω_ki are set to value ρ. For any i not in V_k, the corresponding matrix elements are zero.
* **Experimental Details:** In Liu et al. (2010) the number of groups J is determined as J = floorfunct(p/s). The pivotal rows k are given by the sequence 1, s+1, 2s+1, ...
* **Rho value:** The value of ρ is given as ρ = (1/(s+1)) and in this context, s = 20, thus ρ = 1/21.
* **Number of Hubs g:** We have groups of size s = 20 for p = 40, therefore g = J = floor(p/s) .
* **Hub size:** According to Liu et al. (2010) s = 20.
* **Off-Diagonal Elements of Precision Matrix v:** Represent the strength of the connections in the graph. v =  ρ = (1/(s+1)) = 1/21.
* **Size of Subsampled Data Set:** According to Liu et al. (2010) b(n) = floor(10*sqrt(n))
* **Diagonal Elements of Precision Matrix Ω i.e. u:** According to Liu et al. (2010), the values of the diagonal elements of Ω are set to be one. This means that the variances of each individual variable are set to one. Therefore u = 1.
* **Number of Edges E:** E_l = p - g 
* **Sparsity Level:** Refers to the proportion of non-zero entries in the underlying true graphical model (i.e., the adjacency matrix or precision matrix). This gives an idea of how many edges (connections) are in the true graph compared to the total possible number of edges for a graph of that dimension.
* **Optimal Lambda:**  Determines the amount of penalty applied during the graphical model estimation process. A higher lambda will result in a sparser estimated graph (with fewer edges), while a lower lambda will allow for more edges. The optimal lambda is determined based on the stability of the graph structure across multiple subsamples.
* **Threshold beta:** The beta threshold is a user-defined value that decides the minimum proportion necessary for an edge to be considered "stable" and thus be included in the final graph. For instance, if the threshold is set to 0.1, it means an edge should be present in at least 10% of the subsamples to be considered stable.
* **Adjacency Matrix:** An adjacency matrix is a square matrix used to represent a finite graph. The elements of the matrix indicate whether pairs of vertices are adjacent or not in the graph. For a simple graph (no self-loops or multiple edges) with vertex set V, the adjacency matrix A is a set of |V| x |V| where its element A_ij is 1 or non-negative, if there is an edge between vertix i and vertex j, and 0 otherwise.


## Simulate Synthetic Data
```{r}

#Set Parameters
n <- 400 
p <- 100 
#Size of each hub group
s <- 20
#Number of hub groups
J <- floor(p/s) 
#Off-diagonal elements
rho <- (1/(s+1))
#Subsampled dataset size 
b = (floor(10*sqrt(n)))/n
#Number of Subsamples N
N = 20

set.seed(123)
hub <- generator(n = n, p = p, graph = "hub", rho = rho, g = J, vis = TRUE, verbose = TRUE)

hub_data <- hub$data
true_graph <- as.matrix(hub$theta)
#true_cov <- hub$sigma

#Lambda path
lambda_path  <- getLamPath(max = getMaxCov(hub_data), min = 0.01, len = 40)
lambda <- list(lambda=lambda_path)

#Plot Adjacency Matrix
huge.plot(true_graph)

#hub$omega

```

## StARS, G-StARS and Oracle
```{r}

#Define QUIC as method of choice for stars and gstars
library(QUIC)

quicr <- function(data, lambda, ...) {
  S <- cov(data)
  est <- QUIC(S, rho = 1, path = lambda, msg = 0, tol = 1e-2, ...)
  est$path <- lapply(seq(length(lambda)), function(i) {
  ## convert precision array to adj list
  tmp <- est$X[,,i]; diag(tmp) <- 0
  tmp <- ifelse(tmp != 0, 1, 0)
  return(tmp)
  })
  est
}

#Run pulsar package
library(orca)
out.p <- pulsar(
      data = hub_data,
      fun = quicr,
      fargs = (lambda = lambda),
      criterion = c('stars', 'gcd'),
      thresh = 0.1,
      subsample.ratio = b,
      rep.num = N,
      seed = 123,
      lb.stars = TRUE,
      ub.stars = TRUE,
      ncores = 1,
      refit = FALSE
)

#Get optimal index for gcd
lam_gam <- get.opt.index(out.p, criterion = "gcd")
#Set optimal index for gcd
opt.index(out.p, criterion = "gcd") <- lam_gam


out.p
plot(out.p, scale = T, invlam = FALSE, loglam = FALSE, legends = FALSE)

fit  <- refit(out.p, criterion = c("stars", "gcd"))
print(fit)

stars_graph <- fit[["refit"]][["stars"]]
gstars_graph <- fit[["refit"]][["gcd"]]


# Oracle procedure
oracle_results <- quicr(hub_data, lambda_path)

#Define Hamming Distance as criterium for Oracle
hamming_distance <- function(matrix1, matrix2) {
    return(sum(matrix1 != matrix2))
}

# Minimize total number of different edges between the estimated and true graph
best_lambda_index <- which.min(sapply(1:length(lambda_path), function(i) {
  estimated_graph <- oracle_results$path[[i]]
  hamming_distance(estimated_graph, true_graph)
}))

best_lambda_oracle <- lambda_path[best_lambda_index]

# Extract the oracle precision matrix for the best lambda:
oracle_graph <- oracle_results$X[,,best_lambda_index]

# Convert precision matrix to adjacency matrix
oracle_graph <- ifelse(oracle_graph != 0, 1, 0)
diag(oracle_graph) <- 0


#Plots
huge.plot(stars_graph)
huge.plot(gstars_graph)
huge.plot(oracle_graph)
```

### 1.4) G-Stars: F1-Scores and Jaccard-Index for Hub1
```{r}

# 1. Extract lower triangle
true_graph <- true_graph[lower.tri(true_graph)]
oracle_graph <- oracle_graph[lower.tri(oracle_graph)]
stars_graph <- stars_graph[lower.tri(stars_graph)]
gstars_graph <- gstars_graph[lower.tri(gstars_graph)]

#true_graph
#oracle_graph
#stars_graph 
#gstars_graph

compute_metrics <- function(est_graph, true_graph) {
  TP <- sum(est_graph == 1 & true_graph == 1)
  FP <- sum(est_graph == 1 & true_graph == 0)
  FN <- sum(est_graph == 0 & true_graph == 1)
  TN <- sum(est_graph == 0 & true_graph == 0)

  precision <- TP / (TP + FP)
  recall <- TP / (TP + FN)
  F1 <- 2 * (precision * recall) / (precision + recall)
  jaccard_index <- TP / (TP + FP + FN)
  
  # Calculate Hamming distance
  hamming_distance <- sum(est_graph != true_graph)

  return(list(F1 = F1, Jaccard = jaccard_index, Hamming = hamming_distance))
}

# Now you can compute the metrics including Hamming distance for each graph:
oracle_metrics <- compute_metrics(oracle_graph, true_graph)
cat("Oracle - F1-score:", oracle_metrics$F1, "\n")
cat("Oracle - Jaccard Index:", oracle_metrics$Jaccard, "\n")
cat("Oracle - Hamming Distance:", oracle_metrics$Hamming, "\n\n")

stars_metrics <- compute_metrics(stars_graph, true_graph)
cat("Stars - F1-score:", stars_metrics$F1, "\n")
cat("Stars - Jaccard Index:", stars_metrics$Jaccard, "\n")
cat("Stars - Hamming Distance:", stars_metrics$Hamming, "\n\n")

gstars_metrics <- compute_metrics(gstars_graph, true_graph)
cat("GStars - F1-score:", gstars_metrics$F1, "\n")
cat("GStars - Jaccard Index:", gstars_metrics$Jaccard, "\n")
cat("GStars - Hamming Distance:", gstars_metrics$Hamming, "\n\n")

```

## Loop over all repetitions
```{r}

# Manually set the number of repetitions
num_repetitions <- 2 

# Specify configurations
configs <- list(
  list(n=800, p=40),
  list(n=400, p=100),
  list(n=200, p=200)
)

# Initialize matrices to store F1 scores
F1_stars_matrix <- matrix(0, nrow=num_repetitions, ncol=length(configs))
F1_gcd_matrix <- matrix(0, nrow=num_repetitions, ncol=length(configs))
F1_oracle_matrix <- matrix(0, nrow=num_repetitions, ncol=length(configs))

Jaccard_stars_matrix <- matrix(0, nrow=num_repetitions, ncol=length(configs))
Jaccard_gcd_matrix <- matrix(0, nrow=num_repetitions, ncol=length(configs))
Jaccard_oracle_matrix <- matrix(0, nrow=num_repetitions, ncol=length(configs))

Hamming_stars_matrix <- matrix(0, nrow=num_repetitions, ncol=length(configs))
Hamming_gcd_matrix <- matrix(0, nrow=num_repetitions, ncol=length(configs))
Hamming_oracle_matrix <- matrix(0, nrow=num_repetitions, ncol=length(configs))


for(rep in 1:num_repetitions){
  
  # Function to run experiment
  run_hub <- function(n, p) {
  
    
  # 1.Generate Data  
    
  #Size of each hub group
  s <- 20
  #Number of hub groups
  J <- floor(p/s) 
  #Off-diagonal elements
  rho <- (1/(s+1))
  #Subsampled dataset size 
  b = (floor(10*sqrt(n)))/n
  #Number of Subsamples N
  N = 20

  hub <- generator(n = n, p = p, graph = "hub", rho = rho, g = J, vis = TRUE, 
                   verbose = TRUE)

  hub_data <- hub$data
  true_graph <- as.matrix(hub$theta)
  true_graph <- true_graph[lower.tri(true_graph)]

  #Lambda path
  lambda_path  <- getLamPath(max = getMaxCov(hub_data), min = 0.001, len = 40)
  lambda <- list(lambda=lambda_path)
  
  
  # 2. Estimate StARS and G-StARS
  library(QUIC)

  quicr <- function(data, lambda, ...) {
    S <- cov(data)
    est <- QUIC(S, rho = 1, path = lambda, msg = 0, tol = 1e-2, ...)
    est$path <- lapply(seq(length(lambda)), function(i) {
    ## convert precision array to adj list
    tmp <- est$X[,,i]; diag(tmp) <- 0
    tmp <- ifelse(tmp != 0, 1, 0)
    return(tmp)
    })
    est
  }

  #Run pulsar package
  library(orca)
  out.p <- pulsar(
      data = hub_data,
      fun = quicr,
      fargs = (lambda = lambda),
      criterion = c('stars', 'gcd'),
      thresh = 0.1,
      subsample.ratio = b,
      rep.num = N,
      seed = NULL,
      lb.stars = TRUE,
      ub.stars = TRUE,
      ncores = 1,
      refit = FALSE
  )
  #Get optimal index for gcd
  lam_gam <- get.opt.index(out.p, criterion = "gcd")
  #Set optimal index for gcd
  opt.index(out.p, criterion = "gcd") <- lam_gam

  fit  <- refit(out.p, criterion = c("stars", "gcd"))
  
  stars_graph <- fit[["refit"]][["stars"]]
  gstars_graph <- fit[["refit"]][["gcd"]]

  stars_graph <- stars_graph[lower.tri(stars_graph)]
  gstars_graph <- gstars_graph[lower.tri(gstars_graph)]

  
  # 3. Estimate Oracle
  
  # Oracle procedure
  oracle_results <- quicr(hub_data, lambda_path)

  # Minimize total number of different edges between the estimated and true graph
  best_lambda_index <- which.min(sapply(1:length(lambda_path), function(i) {
    estimated_graph <- oracle_results$path[[i]]
    # Calculate Hamming distance 
    sum(estimated_graph != true_graph)
  }))


  best_lambda_oracle <- lambda_path[best_lambda_index]

  # Extract the oracle precision matrix for the best lambda:
  oracle_graph <- oracle_results$X[,,best_lambda_index]

  # Convert precision matrix to adjacency matrix
  oracle_graph <- ifelse(oracle_graph != 0, 1, 0)
  diag(oracle_graph) <- 0

  oracle_graph <- oracle_graph[lower.tri(oracle_graph)]

  
  # 4. Calculate metrics
 
  # List of estimated graphs
  estimated_graphs <- list(stars = stars_graph, gstars = gstars_graph, 
                           oracle = oracle_graph)

  # Create empty lists to store results
  F1_scores <- list()
  jaccard_indices <- list()
  hamming <- list()

  # Loop through each estimated graph and calculate metrics
  for (name in names(estimated_graphs)) {
  
  # Convert the matrices to binary (1 for edge, 0 for no edge)
  est_bin <- as.numeric(estimated_graphs[[name]] != 0)
  true_bin <- as.numeric(true_graph != 0)

  # Compute true positives, false positives, true negatives, and false negatives
  TP <- sum(est_bin == 1 & true_bin == 1)
  FP <- sum(est_bin == 1 & true_bin == 0)
  TN <- sum(est_bin == 0 & true_bin == 0)
  FN <- sum(est_bin == 0 & true_bin == 1)

  # Calculate precision, recall, F1-score, and Jaccard index
  precision <- TP / (TP + FP)
  recall <- TP / (TP + FN)
  F1 <- 2 * (precision * recall) / (precision + recall)
  jaccard <- TP / (TP + FP + FN)
  # Calculate Hamming distance
  hamming_distance <- sum(estimated_graphs[[name]] != true_graph)

  # Save results to lists
  F1_scores[[name]] <- F1
  jaccard_indices[[name]] <- jaccard
  hamming[[name]] <- hamming_distance
  }
  
 return(list(
  F1_stars = F1_scores[["stars"]],
  F1_gcd = F1_scores[["gstars"]],
  F1_oracle = F1_scores[["oracle"]],
  jaccard_stars = jaccard_indices[["stars"]],
  jaccard_gcd = jaccard_indices[["gstars"]],
  jaccard_oracle = jaccard_indices[["oracle"]],
  hamming_stars = hamming[["stars"]],
  hamming_gcd = hamming[["gstars"]],
  hamming_oracle = hamming[["oracle"]]
  ))

  }

  results <- lapply(configs, function(cfg) run_hub(n = cfg$n, p = cfg$p))  

  # Update the matrices with the results of this repetition
  F1_stars_matrix[rep, ] <- sapply(results, function(x) x$F1_stars)
  F1_gcd_matrix[rep, ] <- sapply(results, function(x) x$F1_gcd)
  F1_oracle_matrix[rep, ] <- sapply(results, function(x) x$F1_oracle)
  
  Jaccard_stars_matrix[rep, ] <- sapply(results, function(x) x$jaccard_stars)
  Jaccard_gcd_matrix[rep, ] <- sapply(results, function(x) x$jaccard_gcd)
  Jaccard_oracle_matrix[rep, ] <- sapply(results, function(x) x$jaccard_oracle)

  Hamming_stars_matrix[rep, ] <- sapply(results, function(x) x$hamming_stars)
  Hamming_gcd_matrix[rep, ] <- sapply(results, function(x) x$hamming_gcd)
  Hamming_oracle_matrix[rep, ] <- sapply(results, function(x) x$hamming_oracle)
    
}

# Compute average scores
avg_F1_stars <- colMeans(F1_stars_matrix)
avg_F1_gcd <- colMeans(F1_gcd_matrix)
avg_F1_oracle <- colMeans(F1_oracle_matrix)

avg_Jaccard_stars <- colMeans(Jaccard_stars_matrix)
avg_Jaccard_gcd <- colMeans(Jaccard_gcd_matrix)
avg_Jaccard_oracle <- colMeans(Jaccard_oracle_matrix)

avg_Hamming_stars <- colMeans(Hamming_stars_matrix)
avg_Hamming_gcd <- colMeans(Hamming_gcd_matrix)
avg_Hamming_oracle <- colMeans(Hamming_oracle_matrix)

desired_order <- sapply(configs, function(x) paste0("n=", x$n, " p=", x$p))

# Update the df to contain the average scores
df <- data.frame(np_setting = desired_order, 
                 F1_stars = avg_F1_stars,
                 F1_gcd = avg_F1_gcd,
                 F1_oracle = avg_F1_oracle)

df_Jaccard <- data.frame(np_setting = desired_order, 
                 Jaccard_stars = avg_Jaccard_stars,
                 Jaccard_gcd = avg_Jaccard_gcd,
                 Jaccard_oracle = avg_Jaccard_oracle)

df_Hamming <- data.frame(np_setting = desired_order, 
                 Hamming_stars = avg_Hamming_stars,
                 Hamming_gcd = avg_Hamming_gcd,
                 Hamming_oracle = avg_Hamming_oracle)

df$np_setting <- factor(df$np_setting, levels = desired_order, ordered = TRUE)
df_Jaccard$np_setting <- factor(df_Jaccard$np_setting, levels = desired_order, ordered = TRUE)
df_Hamming$np_setting <- factor(df_Hamming$np_setting, levels = desired_order, ordered = TRUE)


```

## Plotting F1-Scores over all repetitions for all configurations
```{r}

library(ggplot2)

# Plotting the results
ggplot(df, aes(x=np_setting)) + 
  geom_line(aes(y=F1_stars, color="Stars", group="Stars"), linetype="dotted", color="lightblue", linewidth=1.5) + 
  geom_line(aes(y=F1_gcd, color="GCD", group="GCD"), linetype="dotted", color="darkorange", linewidth=1.5) + 
  geom_line(aes(y=F1_oracle, color="Oracle", group="Oracle"), linetype="solid", color="black", linewidth=1.5) + 
  geom_point(aes(y=F1_stars, color="Stars"), size=1.5) +
  geom_point(aes(y=F1_gcd, color="GCD"), size=1.5) +
  geom_point(aes(y=F1_oracle, color="Oracle"), size=1.5) +
  labs(title = "Hub", y = "F1-score") + 
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 14)) + 
  scale_color_manual(values=c("Stars"="lightblue", "GCD"="darkorange", "Oracle"="black"), 
                     name="Method",
                     breaks=c("Stars", "GCD", "Oracle"))

# Plotting the results
ggplot(df_Jaccard, aes(x=np_setting)) + 
  geom_line(aes(y=Jaccard_stars, color="Stars", group="Stars"), linetype="dotted", color="lightblue", linewidth=1.5) + 
  geom_line(aes(y=Jaccard_gcd, color="GCD", group="GCD"), linetype="dotted", color="darkorange", linewidth=1.5) + 
  geom_line(aes(y=Jaccard_oracle, color="Oracle", group="Oracle"), linetype="solid", color="black", linewidth=1.5) + 
  geom_point(aes(y=Jaccard_stars, color="Stars"), size=1.5) +
  geom_point(aes(y=Jaccard_gcd, color="GCD"), size=1.5) +
  geom_point(aes(y=Jaccard_oracle, color="Oracle"), size=1.5) +
  labs(title = "Hub", y = "Jaccard-score") + 
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 14)) + 
  scale_color_manual(values=c("Stars"="lightblue", "GCD"="darkorange", "Oracle"="black"), 
                     name="Method",
                     breaks=c("Stars", "GCD", "Oracle"))

# Plotting the results
ggplot(df_Hamming, aes(x=np_setting)) + 
  geom_line(aes(y=Hamming_stars, color="Stars", group="Stars"), linetype="dotted", color="lightblue", linewidth=1.5) + 
  geom_line(aes(y=Hamming_gcd, color="GCD", group="GCD"), linetype="dotted", color="darkorange", linewidth=1.5) + 
  geom_line(aes(y=Hamming_oracle, color="Oracle", group="Oracle"), linetype="solid", color="black", linewidth=1.5) + 
  geom_point(aes(y=Hamming_stars, color="Stars"), size=1.5) +
  geom_point(aes(y=Hamming_gcd, color="GCD"), size=1.5) +
  geom_point(aes(y=Hamming_oracle, color="Oracle"), size=1.5) +
  labs(title = "Hub", y = "Hamming-score") + 
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 14)) + 
  scale_color_manual(values=c("Stars"="lightblue", "GCD"="darkorange", "Oracle"="black"), 
                     name="Method",
                     breaks=c("Stars", "GCD", "Oracle"))

```

## Alternative Plots
```{r}

# Create custom labels for configurations
config_labels <- sapply(configs, function(cfg) paste("p =", cfg$p, "\nn =", cfg$n))
names(config_labels) <- sapply(configs, function(cfg) paste("n", cfg$n, "p", cfg$p, sep = "_"))

# Set factor levels for 'Config' in data frames with custom labels
mean_f1_df$Config <- factor(mean_f1_df$Config, levels = names(config_labels), labels = config_labels)
mean_hamming_df$Config <- factor(mean_hamming_df$Config, levels = names(config_labels), labels = config_labels)


# Plotting F1 scores
F1_Hub <- ggplot(mean_f1_df, aes(x = Config, y = Mean_F1, color = Method)) +
  geom_line(aes(group = Method), linetype = "dotted", size = 1.5) + 
  geom_point(size = 1.5) +
  geom_errorbar(aes(ymin = CI_Lower, ymax = CI_Upper), width = 0.1, alpha = 0.5) +
  geom_text(aes(label = paste(# "Lamb. =", round(mean_lambda_df$Mean_Lambda, 3), 
                              "", round(mean_sparsity_df$Mean_Sparsity, 3))), 
            vjust = -0.9, position = position_dodge(width = 0.8), size = 3) +
  labs(title = "Hub F1 Scores", y = "Mean F1 Score", x = "") +  
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
        axis.title.x = element_blank(),
        legend.title = element_blank()) +
  scale_color_manual(values = c("Stars" = "lightblue", "GStars" = "darkorange", "Oracle" = "black"))

# Plotting Hamming distances
Hamming_Hub <- ggplot(mean_hamming_df, aes(x = Config, y = Mean_Hamming, color = Method)) +
  geom_line(aes(group = Method), linetype = "dotted", size = 1.5) + 
  geom_point(size = 1.5) +
  geom_errorbar(aes(ymin = CI_Lower, ymax = CI_Upper), width = 0.1, alpha = 0.5) +
  geom_text(aes(label = paste(# "Lamb. =", round(mean_lambda_df$Mean_Lambda, 3), 
                              "", round(mean_sparsity_df$Mean_Sparsity, 3))), 
            vjust = -1, position = position_nudge(y = 0.8), angle = 30, size = 3) +
  labs(title = "Hub Hamming Distances", y = "Mean Hamming Distance", x = "") +  
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 14),
        axis.title.x = element_blank(),
        legend.title = element_blank()) +
  scale_color_manual(values = c("Stars" = "lightblue", "GStars" = "darkorange", "Oracle" = "black"))

# Save the plots
ggsave(filename = "F1_Hub_Plot.pdf", plot = F1_Hub, path = dir_path4, width = 8, height = 6, dpi = 300)
ggsave(filename = "Hamming_Hub_Plot.pdf", plot = Hamming_Hub, path = dir_path4, width = 8, height = 6, dpi = 300)

# Display the plots
F1_Hub
Hamming_Hub

```
